PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-04-27 paper/ms.tex
add words to describe RUWE test

>>>>

Performing the same analysis using the renormalized unit weight error
(RUWE\footnote{ See the Gaia DPAC technical note
GAIA-C3-TN-LU-LL-124-01,
\url{http://www.rssd.esa.int/doc_fetch.php?id=3757412}, accessed
2020-04-27. }) rather than the reduced $\chi^2$ yielded similar
results.  \ptfo\ has a RUWE of 1{.}22, which corresponds to the
93$^{\rm rd}$ percentile of 25$\,$Ori-1 members.  Two of thirty stars
with variability amplitudes greater than 9.7\% showed higher RUWE.
One was CVSO~35, which has a TESS light-curve that varies by 2
magnitudes, and shows a strong IR excess and a 10$\mu$m silicate emission
feature \citep{mauco_herschel_2018}.  The other is GAIA DR2
3222210363837122048.
